---
output: md_document
---

# R Implementation Pattern

Simple Pie Chart is a graphic

Then it shows an example of R pattern implementation.

## Data Set

For this example it will be used Data Set called mtcars, this data set is the R default data set this data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)

```

## Dependencies 
Graphics - default package on R
Ggplot2 
Lattice
## Code example 

### Code Example With Graphics
```{r}
cars <- (mtcars$wt)
plot(cars, type="o", col="blue")
title(main="Cars", col.main="blue", font.main=4)
```
### Code Example With Ggplot
```{r}
head(mtcars)
library(ggplot2)
ggplot(data=mtcars, aes(x=mtcars$wt, y=mtcars$mpg))+
  geom_line()+
  geom_point()

```
### Code Example With Lattice
```{r}
library(lattice)
panel.spline <- function(x, y) {
  panel.xyplot(x, y) 
  panel.loess(x, y) 
}
attach(mtcars)
xyplot(mpg~wt, scales=list(cex=2, col="red"),
       panel=panel.spline)
```