---
output: md_document
---

# R IMPLEMENTATION

For implementation of pattern Tree Diagram in R, it use the package "diagram".  This package include functions for visualises simple graphs (networks) based on a transition matrix, utilities to plot flow diagrams, visualising webs, electrical networks, ...  (Soetaert, 2014)[^1].  


## Data Set

For this proyect it will use the dataset mtcars.

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)

```


## Dependences

* diagram


## Code Example


### Diagram


```{r}
library(diagram)
par(mfrow=c(1,1))
par(mar=c(0,0,0,0))
openplotmat(main="Tree Diagram ")
x<-subset(mtcars, mtcars$cyl==4)
y<-subset(mtcars, mtcars$cyl==6)
z<-subset(mtcars, mtcars$cyl==8)
elpos<-coordinates (c(1,1,7))
treearrow(from=elpos[1,],to=elpos[2,],lwd=4)  
treearrow(from=elpos[2,],to=elpos[3:9,],lwd=4) 
labs<-c("Car Distribution \n by Cylindres", "6 Cylindres",  row.names(y))
for ( i in 1:length(labs)) textrect(elpos[i,],radx=0.06,rady=0.05,lab=labs[i] ,cex=0.6, col = "blue", box.col="grey")

```
The complete online documentation is also available in the form of a single [PDF](https://cran.r-project.org/web/packages/diagram/diagram.pdf) file at CRAN.

From within R, type:
> help(diagram)


## References

[^1]: Soetaert, Karline (2014). CRAN. Consultado el 12 de Mayo, 2016 en https://cran.r-project.org/web/packages/diagram/index.html
