---
output: md_document
---

# R IMPLEMENTATION

For implementation of pattern Tree Map in R, it use the package "treemap".  A treemap is a space-filling visualization of hierarchical structures. This package offers great flexibility to draw treemaps (Tennekes, 2016)[^1].   


## Data Set

For this proyect it will use the dataset mtcars.

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)

```


## Dependences

* **Treemap**


## Code Example


### Treemap


```{r}
library(treemap)
treemap(mtcars,
index=c("cyl", "gear"),
vSize="cyl", title="Tree Map by Cylindres and Gears")

```
The complete online documentation is also available in the form of a single [PDF](https://cran.r-project.org/web/packages/treemap/treemap.pdf) file at CRAN.

From within R, type:

> help(treemap)


## References

[^1]:  Tennekes, Martijn (2016). CRAN. Consultado el 16 de Mayo, 2016 en https://cran.r-project.org/web/packages/treemap/index.html
