---
output: md_document
---

# R Implementation Pattern

Sankey Diagram is a graphic that contains intputs an ouputs, they represent a sum respectively. In such diagrams, it is easy to see representations of the efforts of input and output.

## Data Set

For this example it will be used Data Set called mtcars, this data set is the R default data set this data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)

```

## Dependencies 

> Graphics - default package on R

For this example in graphics it will be used other dependence called Sankey.R
this dependence is hosted in this link:  [https://gist.github.com/aaronberdanier/1423501#file-sankey-r]

> GoogleVis 

## Code example 

### Code Example With Graphics

```{r}
source('Sankey.R')

mpg=mtcars["Datsun 710",1]
hp=mtcars["Datsun 710",4]
cyl=mtcars["Datsun 710",2]
wt= mtcars["Datsun 710",6]
disp=mtcars["Datsun 710",3]
qsec=mtcars["Datsun 710",7]
gear =mtcars["Datsun 710",10]
inputs = c(mpg,disp)
losses = c(qsec,gear,cyl,hp)
unit = "n ="

labels = c("Miles/(US) gallon",
           "Displacement\n",
           "1/4 mile time",
           "Number of forward gears",
           "Number of cylinders",
           "Datsun 710\nGross HP")

SankeyR(inputs,losses,unit,labels)

# Clean up my mess
rm("inputs", "labels", "losses", "SankeyR", "unit")

```

### Code Example With GoogleVis

In this example, a package called GoogleVis google for R is used, this package generates Web graphics can also be used in desktop applications.

```{r}

require(googleVis)
mpg=mtcars["Datsun 710",1]
hp=mtcars["Datsun 710",4]
cyl=mtcars["Datsun 710",2]
wt= mtcars["Datsun 710",6]
disp=mtcars["Datsun 710",3]
qsec=mtcars["Datsun 710",7]
gear =mtcars["Datsun 710",10]
dat <- data.frame(From=c(rep("Miles/(US) gallon",4), rep("Displacement", 4)),
                  To=c(rep(c("1/4 mile time",
                             "Number of forward gears",
                             "Number of cylinders",
                             "Datsun 710 Gross horsepower"))),
                  Weight=c(mpg,gear,cyl,hp))

sk1 <- gvisSankey(dat, from="From", to="To", weight="Weight")
plot(sk1)

```