---
output: md_document
---

# R IMPLEMENTATION

R is a language and environment for statistical computing and graphics. It is a GNU project which is similar to the S language and environment which was developed at Bell Laboratories (formerly AT&T, now Lucent Technologies) by John Chambers and colleagues. 
R provides a wide variety of statistical (linear and nonlinear modelling, classical statistical tests, time-series analysis, classification, clustering, …) and graphical techniques, and is highly extensible (The R Fundation, 2016)[^1].


## Data Set

For this proyect it was use the dataset mtcars. This data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
counts <- table(mtcars$cyl, mtcars$gear)
counts

```


## Dependences

* **LatticeExtra**. Building on the infrastructure provided by the lattice package, this package provides several new high-level functions and methods, as well as additional utilities such as panel and axis annotation functions. (Sarkar, 2016)[^2]



## Code Example


### Lattice

```{r}
d <- table(mtcars$gear, mtcars$cyl)
data<-as.data.frame(d)
names(data)<-c("Gears","Cylindres","Frequency")
data$Gears
library(latticeExtra)
cloud(Frequency~Gears+Cylindres, data, panel.3d.cloud=panel.3dbars, col.facet='grey', 
      xbase=0.4, ybase=0.4, scales=list(arrows=FALSE, col=1), main="Car Distribution by Gears and Cyl", 
      par.settings = list(axis.line = list(col = "transparent")))

```

The complete online documentation is also available in the form of a single [PDF](https://cran.r-project.org/web/packages/latticeExtra/latticeExtra.pdf) file at CRAN. 


## References

[^1]: The R Fundation. (s.f). R.Consultado el 3 de marzo, 2016 en https://www.r-project.org/about.html.
[^2]: Sarkar, Deepayan (2016). R. Consultado el 5 de marzo, 2016 en https://cran.r-project.org/web/packages/latticeExtra/latticeExtra.pdf
