---
output: md_document
---

# R Implementation Pattern

A multiple line chart is a graphic in which show multiple data series and allows a more graphic visual comparison between the different data groups. 

## Data Set

For this example it will be used Data Set called mtcars, this data set is the R default data set this data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)

```

## Dependencies 

> Graphics - default package on R
> Ggplot2 
> Lattice

## Code example 

### Code Example With Graphics

```{r}
carb <- mtcars$carb
cyl <- mtcars$cyl

plot(carb, type="o", col="blue", ylim=c(0,10))

lines(cyl, type="o", pch=22, lty=2, col="red")

title(main="Mtcars", col.main="Blue", font.main=4)

```

### Code Example With Ggplot

```{r}
library(ggplot2)

df2 <- mtcars
ggplot(data=df2, aes(x=mpg, y=hp, group=gear)) +
  geom_line()+
  geom_point()
  
```

### Code Example With Lattice

```{r}

library(lattice)
L = mtcars$am == 0 
Camaro=mtcars["Camaro Z28",]
Datsun=mtcars["Datsun 710",]
x= 1:11
df <- data.frame(Camaro = Camaro, Datsun = Datsun, x = x)
xyplot(Camaro + Datsun  ~ x, data = df, type = "o", auto.key=TRUE)

```