---
output: md_document
---

# R Implementation Pattern

implementacion del patron en R

## Data Set

For this example it will be used Data Set called mtcars, this data set is the R default data set this data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)

```

## Dependencies 

> Graphics - default package on R

For this example in graphics it will be used other dependence called plot_area.
this dependence is hosted in this link:  [https://gist.github.com/fawda123/6589541/raw/8de8b1f26c7904ad5b32d56ce0902e1d93b89420/plot_area.r]

> Ggplot2 

## Code example 

### Code Example With Graphics

```{r}
source('Continuous Quantities/plot_area.r')
datos<-data.frame(mtcars$cyl,mtcars$mpg)
plot.area(datos,prop=F,horiz=T)
```

### Code Example With Ggplot2

```{r}
library(ggplot2)
data.set <- data.frame(
  Type = c(rep(mtcars$mpg, 2),rep(mtcars$cyl, 2)),
  Comparacion = rep(c('Millas por galón', 'Cilindros'), 2),
  Value = rpois(32, 20)
)

qplot(Type, Value, data = data.set, fill = Comparacion, geom = "area")

```